---
title: "ADSC2030 Incomplete Block Designs Examples"
author: "Sean Hellingman"
format: pdf
editor: visual
---

# Part I

## Example 1 from slides

```{r}

library(daewr)







```

## Example 2 from slides

```{r}

library(AlgDesign)

# BIBsize(t,k)

# BIB <- optBlock( ~., withinData = factor(1:t),blocksizes = rep(k,b))
# 
# des <- BIB$rows
# dim(des) <- NULL
# 
# des <- matrix(des, nrow = b, ncol = k, byrow = TRUE,
# dimnames = list(c("Block1", ..., "Blockb"), c("unit1", ..., "unitk")))
# 
# des



```

## Example 3 from slides

```{r}
library(lsmeans)

## 1 ##
data(taste)


## 2 ##

# model <- aov(response ~ block + factor, data = data)

## 3 ##

# lsmeans(model, pairwise ~ factor, adjust = ("tukey"))




```

## Example 4 from slides

```{r}





```

# Part II

## Example 1 from slides

```{r}

library(daewr)
library(lsmeans)

data(BPmonitor)





# model <- aov(response ~ block + factor, data = data)
# summary(model)
# 
# 
# lsmeans(model, pairwise ~ factor, adjust = ("tukey"))

```

## Example 2 from slides

```{r}


set.seed(2030)
library(agricolae)
# library(knitr)



# treat <- c(1, ..., t)
# des <- design.cyclic(treat, k = k, r = r)
# des$book
#kable(des$book)


```

## Example 3 from slides

```{r}

set.seed(2030)



# treat <- c(1, ..., t)
# RCD <- design.cyclic(treat, k = k, r = r, rowcol = TRUE)
# RCD$book


```

## Example 4 from slides

**From Example 5 (Randomized Block Designs II):**

The purpose was to test the bioequivalence of three formulations (A=solution, B=tablet, C=capsule) of a drug as measured by the AUC (Area Under the Curve) as it relates to the concentration of the drug in the blood as a function of time since consumption.

Three subjects (people) took each formulation of the drug with appropriate *washout* periods between and the AUC was calculated based on blood samples.

Each subject is treated as a block as individuals will metabolize drugs differently. Due to the nature of the study, trials at different times, the period was also selected as a block.

**Added 3 more formulations of the drug (D = Injection, E = Inhaler, F = Topical)\
Each subject still only received formulations, therefore 3 more subjects were needed.**

```{r}

RCD <- read.csv("RCD.csv")




# model5 <- aov(AUC ~ Subject + Period + Treat, data = data)
# summary(model5)


# lsmeans(model, pairwise ~ factor, adjust = ("tukey"))


```
