---
title: "ADSC2030 Completely Randomized Designs with One Factor Examples"
author: "Sean Hellingman"
format: html
editor: visual
---

# Part I

## Illustrative Example 1B from slides

Treatment factor:\
Experimental unit:\
Response:\
Other factors to be held constant:

## Example 1 from slides

```{r}

set.seed(7638) # reproducibility 




```

## Illustrative Example 2 from slides

1 Objectives:\
2 Experimental Units:\
3 Response/Dependent Variable:\
4 Independent and Lurking Variables:\
5 Pilot Tests (hypothetical):\
6 Choose Experimental Design:\
7 Determine the number of Replicates:\
8 Randomize Experimental Units to Treatment Levels:

## Example 2 from slides

```{r}
#Height <- c(6.5,9.75,6.5,4.5,10.5,5.0,5.50,6.75,9.50,8.75,6.50,8.25)

library(daewr)
data('bread')



```

## Example 3 from slides

```{r}

library(gmodels)
#fit.contrast()


```

## Example 4 from slides

```{r}



```

# Part II

## Example 1 from slides

```{r}

library(car)


```

## Example 2 from slides

```{r}

library(MASS)

boxcox(lm2)

```

## Example 3 from slides

```{r}






```

## Example 4 from slides

min:\
max:\
Delta:\
Alpha:\
Sigma:

```{r}

library(daewr)


# rmin <- 
# rmax <- 
# alpha <- rep(,rmax - rmin + 1)
# sigma <- sqrt()
# nlevels <- t #3
# nreps <- rmin:rmax
# Delta <-  #Chosen by us
# power <- Fpower1(alpha,nlevels,nreps,Delta,sigma)
# 
# power #results


#Fpower()

```

## Example 5 from slides

```{r}

library(daewr)

# 1 #


# #H0: mu45 = 1/2(mu35 + mu40)
# 
# fit.contrast(anov1,"time", )
# 
# #0: mu35 = mu40
# 
# fit.contrast(anov1,"time", )



# con <- matrix(c(1, -1/3, -1/3, -1/3, 0, 1, -1, 0, 0, 0,
# 1, -1 ), byrow = TRUE, nrow = 3) # row matrix of comparisons


# # 2 #
# 
# contrasts() <- contr.poly(3)
# contrasts()




```

## Example 6 from slides

```{r}

## Tukey's ##

# model <- aov(response ~ factor, data=data)
# model.tukey <- TukeyHSD(model,ordered = TRUE) # All
# pairs
# model.tukey # Print results



## N-K ##

# library(agricolae)
# model <- aov(response ~ factor, data=data)
# compare <- SNK.test(model,"factor",alpha = 0.05)
# compare # Print results




```

## Example 7 from slides

```{r}

library(multcomp)

#glht() 

# relevel(data$variable, ref = "New.Reference") # to re-order if needed

# results.dun <- glht(model, linfct = mcp(time = "Dunnett"),
#                     alternative = "greater")
# 
# summary(results.dun)

```

## Exercises

```{r}

# set.seed(2030) #Reproducibility
# r <- 5
# t <- 4
# n <- t*r
# 
# f <- factor(rep( c("25", "30", "35", "40"), each= r)) #Repeat the factor levels for r replications
# fac <- sample(f, t*r) #Randomization
# eu <- 1:n #index for each experimental unit
# plan <- data.frame(Unit = eu, FactorLevel = fac) 




```
