---
title: "ADSC2030 Factorial Designs I II Examples"
author: "Sean Hellingman"
format: pdf
editor: visual
---

## Illustrative Example 1

Experimental unit:\
Difference between replicates and duplicates for this design:\
Treatment factor:\
Possible lurking variables:\
Why randomize:

## Example 1 from slides

```{r}

library(ggplot2)
library(MASS)

Bread <- read.csv("Bread.csv")
colnames(Bread)

#ggplot(data=Bread,mapping = aes(x = , y = , color = )) +
#  geom_point()+
#  labs(title = "",
#       x = "",
#       y = "")+ 
#  geom_smooth() #Add curve to plot

```

Code for two-factor randomization:

```{r}


D <- expand.grid(Factor.1=as.factor(c("A","B","C","D")),
                 Factor.2=as.factor(c("E","F","G","H")))

D <- rbind(D,D)

set.seed(2591)
D <-D[order(sample(1:nrow(D))), ] 

```

## Example 2 from slides

```{r}




```

## Example 3 from slides

```{r}

library(daewr)
data("COdata")


```

## Example 4 from slides

```{r}




```

## Example 5 from slides

```{r}

# model.tables(model, type = "means", se = T )

```

```{r}
library(gmodels)

c1 <-c(-1/2, 0, 1/2) 
c2 <-c(.5, -1, .5)
cm <-cbind( c1, c2 )

mod2 <- aov( CO ~ Eth * Ratio, contrasts = list(Eth = cm, Ratio = cm ), data = COdata) 

summary(mod2)

c <- rbind('Ethanol 0.3 vs 0.1' = c(0,1,0,0,0,0,0,0,0), 'Ratio 16 vs 14' = c(0,0,0,1,0,0,0,0,0) ) 

estimable(mod2,c)

#lm1 <- lm(CO ~ Eth + Ratio + Eth:Ratio, data = COdata)
#summary(lm1)

#c(1,0,0,0,0,0,0,0,0)
#c(0,0,0,0,1,0,0,0,0)
```

-   The first three elements (0, 0, 0) correspond to the intercept and the main effects of the "Eth" factor for the levels 0.2 and 0.3.

-   The next two elements (0, 0) correspond to the main effects of the "Ratio" factor for the levels 15 and 16.

-   The last four elements (0, 0, 0, 0) correspond to the interaction terms between "Eth" and "Ratio."

## Example 6 from slides

```{r}



```

### Interaction Plots

```{r}

with(COdata, (interaction.plot(Eth, Ratio, CO, type =
"b", pch = c(18,24,22), leg.bty = "o", main =
"Interaction Plot of Ethanol and air/fuel ratio",
xlab = "Ethanol",ylab = "CO emissions")))



```

It is clear that an interaction exists due to the modulated effects of the ethanol levels on the CO emissions for each ratio.

## Example 7 from slides

```{r}




```

## Example 8 from slides

```{r}



```

## Example 9 from slides

```{r}

COdatam <- COdata 
COdatam[18, 3] <- NA # remove one observation



```

## Example 10 from slides

#### Data:

```{r}

Cellmeans <-tapply( COdata$CO, list(COdata$Eth, COdata$Ratio) , mean ) 
dim(Cellmeans) <-NULL 
Eth <-factor(rep(c(.1, .2, .3), 3)) 
Ratio <-factor(rep(c(14,15,16), each=3)) 
cells <-data.frame(Cellmeans, Eth, Ratio) # Use cells 




```

#### Method I

```{r}



```

#### Method II

## Example 11 from slides

```{r}


library(dplyr)
library(daewr)
data("virus")

 



```
